### 2014-07-01 Quality_Reports/PCR_bottleneck.Rmd
Changed the PBC code, to be based on table and include a cap

```{r PBC_fun,include = TRUE,results = "hide",echo = TRUE}
PBC <- function(file)
{
  require(GenomicAlignments)
  rr = readGAlignmentsFromBam(file,param = NULL)
  ss1 = subset(rr,subset =strand(rr)=="+")
  ss2 = subset(rr,subset = strand(rr)=="-")
  N11 = length(unique(start(ss1)))
  N12 = length(unique(end(ss2)))
  N1 = N11+N12
  Nd1 = length(ss1)
  Nd2 = length(ss2)
  Nd = Nd1 + Nd2
  PBC1 = round(N11 / Nd1,4)
  PBC2 = round(N12 / Nd2,4)
  PBC = round(N1 /Nd,4)
  return(c(PBC_plus=PBC1,PBC_minus=PBC2,PBC=PBC))  
}
```

@@

We can see:
- The overall level of the ChIP-Exo's PBC coefficients is lower than the level of the other two ChIP-Seq labels
- The range of the ChIP-Exo's PBC coefficients is also smaller than other two ranges. In particular, the interquartile range of the PET coefficients is smaller than the interquartile range of the SET coefficients.

>>>>

```{r PBC_fun,include = TRUE,results = "hide",echo = TRUE}
PBC <- function(file,cap = Inf)
{
  require(GenomicAlignments)
  message(file)
  rr = readGAlignmentsFromBam(file,param = NULL)
  ss1 = subset(rr,subset =strand(rr)=="+")
  ss2 = subset(rr,subset = strand(rr)=="-")
  tab1 = table(start(ss1))
  tab2 = table(end(ss2))
  tab = table(c(start(ss1),end(ss2)))
  PBC1 = round(sum(tab1 == 1)/sum(tab1 >= 1 & tab1 <= cap),4)
  PBC2 = round(sum(tab2 == 1)/sum(tab2 >= 1 & tab2 <= cap),4)
  PBC = round(sum(tab == 1) / sum(tab >= 1 & tab <= 4),4)
  message("PBC +:",PBC1)
  message("PBC -:",PBC2)
  message("PBC:",PBC)
  return(c(PBC_plus=PBC1,PBC_minus=PBC2,PBC=PBC))  
}
```

@@

We can see:
- The overall level of the ChIP-Exo's PBC coefficients is lower than the level of the other two ChIP-Seq labels
- The level of ChIP-Seq PET is higher that the level of both SET generated y ChIP-Seq and ChIP-Exo
